Active-contours driven registration of diffusion MR images of the brain

### 2015-03-16 Publications/2015-NeuroImage/05-results.tex
introducing final results

\paragraph*{Evaluation \& cross-comparison}\label{sec:res_cc_evaluation}
%
Finally, we tested the performance of our registration method, and compared it to the
  a standard \gls*{t2b} correction.
For both \emph{regseg} and the \gls*{t2b} methods, we computed the \gls*{swindex} \eqref{eq:swindex}
  of every surface.
Finally, to statistically compare the results, we performed a one-way ANOVA test
  on the warping indices for three surfaces.
Following the nomenclature introduced in section \autoref{sec:human_connectome}, we selected
  $\Gamma_{VdGM}$, $\Gamma_{WM}$, and $\Gamma_{pial}$ as surfaces of interest.
These interfaces are critical in connectivity analyses, and small errors in their location may
  lead to discarding fundamental paths between regions.
We also reported the 95\% CIs of the warping indices for those surfaces.
The quantitative results of the ANOVA tests and the CIs are presented in \autoref{tab:results_real}.
Visual assessment of one case is shown in \autoref{fig:results_real}, along with the corresponding
  box plots of error distributions by correction method and surface.
Extended visual assessment of the 16 cases is aggregated in the \suppl{section S4}.

\begin{table}
		\centering
		\footnotesize
		\tabcolsep=0.05cm
    \begin{tabular}{L{1.8cm}ccc}
                            & $\Gamma_{VdGM}$  & $\Gamma_{WM}$ & $\Gamma_{pial}$ \\
    \hline
    CI \emph{regseg}        & 0.39 - 0.64 & 0.64 - 0.83 & 0.76 - 0.93 \\
    CI competing            & 2.36 - 3.37 & 2.65 - 3.19 & 2.82 - 3.40 \\
    \hline
    ANOVA (f-stat/p-value)  & (51.81/1.5e-06) & (148.25/8.1e-10) & (143.01/1.1e-09) \\
    \hline
    \end{tabular}
    \caption{All the 95\% CIs of the \gls*{swindex} distributions computed for the
      surfaces of interest were lower for \emph{regseg} with respect to the competing
      method.
    CIs reported in this table were computed using bootstrapping with mean as location
      statistic and $10^4$ samples.
    One-way-ANOVA tests indicated that there is a significant difference between our method and
      the competing method of choice.
    }\label{tab:results_real}
\end{table}

>>>>

\paragraph*{Evaluation \& cross-comparison}\label{sec:res_cc_evaluation}
%
Finally, we tested the performance of our registration method, and compared it to the
  a standard \gls*{t2b} correction.
We computed the \gls*{swindex} \eqref{eq:swindex} of every surface after correction,
  for both \emph{regseg} and the \gls*{t2b} methods.
Finally, to statistically compare the results, we performed a one-way ANOVA test
  on the warping indices for three specific surfaces of interest
  ($\Gamma_{VdGM}$, $\Gamma_{WM}$, and $\Gamma_{pial}$).
These interfaces are critical in analyses on whole-brain tractography.
The one-way ANOVA evidenced that error distributions were significantly different,
  $p \approx 2 \times 10^{-9}$.
We also reported the 95\% CIs of the \gls*{swindex} for those surfaces.
The aggregated CI for \emph{regseg} was $[1.08 - 1.50] mm$, whereas the competing method
  yielded an aggregated CI of $[2.06 - 2.43] mm$.
The quantitative results of the ANOVA tests and the CIs are presented in \autoref{tab:results_real}.
Visual assessment of one case is shown in \autoref{fig:results_real}, along with the corresponding
  box plots of error distributions by correction method and surface.
Extended visual assessment of the 16 cases is included in the \suppl{section S4}.

\begin{table}
		\centering
		\footnotesize
		\tabcolsep=0.05cm
    \begin{tabular}{cccccc}
    & & $\Gamma_{VdGM}$  & $\Gamma_{WM}$ & $\Gamma_{pial}$ & Aggregated \\
    \hline
    \multirow{2}{*}{CI}
       & \emph{regseg}        & 0.77 - 1.18 & 0.95 - 1.85 & 1.33 - 2.13 & 1.08 - 1.50 \\
       & T2B                  & 1.73 - 2.62 & 1.96 - 2.40 & 2.16 - 2.63 & 2.06 - 2.43 \\
    \hline
    \multirow{2}{*}{ANOVA}
       & p-value  & 1.4$\times$10$^{-5}$& 1.3$\times$10$^{-3}$& 2.5$\times$10$^{-3}$ & 2$\times$10$^{-9}$ \\
       & f-stat   & 27.87               & 12.89               & 11.13                & 45.04 \\
    \hline
    \end{tabular}
    \caption{All the 95\% CIs of the \gls*{swindex} distributions computed for the
      surfaces of interest were lower for \emph{regseg} with respect to the competing
      method.
    CIs reported in this table were computed using bootstrapping with mean as location
      statistic and $10^4$ samples.
    One-way-ANOVA tests indicated that there is a significant difference between our method and
      the competing method of choice.
    }\label{tab:results_real}
\end{table}

### 2015-03-16 Publications/2015-NeuroImage/06-discussion.tex
introducing final results

\paragraph*{Application on real data}
After a preliminary experiment to demonstrate the aptness of our segmentation model
  in section \autoref{sec:res_model_and_metric}, we evaluated \emph{regseg} in
  a real environment, using the experimental framework presented in \autoref{fig:evworkflows}.
We processed 16 subjects from the \gls*{hcp} database with both \emph{regseg}
  and an in-house replication of a competing method.
This alternative approach solves distortion using \emph{b0}-to-\gls*{t2} registration.
Our method presented significantly different results (ANOVA tests are reported in
  \autoref{tab:results_real}), and the 95\% CIs revealed the high accuracy of
  \emph{regseg}.
The aggregated CI for \emph{regseg} was $[0.39 - 0.93] mm$, whereas the competing method
  yielded an aggregated CI of $[2.36 - 3.40] mm$.
Even though we carefully configured the competing method by using the same algorithm and
  extending the same settings from a widely used software, cross-comparison
  experiments are prone to the so-called instrumentation bias \citep{tustison_instrumentation_2013}.
Therefore, these results do not show that the \emph{regseg} software \emph{is} better than the
  competing method, but they are communicated to proof that \emph{regseg} is a solid option to
  correct \gls*{dmri} data for distortions, and any other potential application.

>>>>

\paragraph*{Application on real data}
After a preliminary experiment to demonstrate the aptness of our segmentation model
  in section \autoref{sec:res_model_and_metric}, we evaluated \emph{regseg} in
  a real environment, using the experimental framework presented in \autoref{fig:evworkflows}.
We processed 16 subjects from the \gls*{hcp} database with both \emph{regseg}
  and an in-house replication of the \gls*{t2b} correction method.
Our method presented significantly different results (ANOVA tests are reported in
  \autoref{tab:results_real}), and the 95\% CIs revealed the high accuracy of
  \emph{regseg}.
Even though we carefully configured the competing method by using the same algorithm and
  extending the same settings from a widely used software, cross-comparison
  experiments are prone to the so-called instrumentation bias \citep{tustison_instrumentation_2013}.
Therefore, these results do not show that the \emph{regseg} software \emph{is} better than the
  competing method, but they are communicated to proof that \emph{regseg} is a solid option to
  correct \gls*{dmri} data for distortions, and any other potential application.
